Nodal Discontinuous Galerkin Method for the Two-Moment Model of Neutrino Transport

### 2017-04-14 Documents/M1/dgM1Curvilinear.tex
Committed as a sample of neutrino opacity section.

\ee{Ran write about tabulated B85 absorption and scattering opacities.}

>>>>

%\ee{Ran write about tabulated B85 absorption and scattering opacities.}

Given by \citet{bruenn_1985}, the absorption opacity of neutrino $\chi$ 
\begin{equation}
  \chi(\epsilonNu,\bU) = \dfrac{1}{\lambda(\epsilonNu,\bU)} + j(\epsilonNu,\bU), 
\end{equation}
where $j(\epsilonNu,\bU) $ is the neutrino emissivity
\begin{equation}
j = j_{nucleon} + j_{nuclear},
\end{equation}  
and $\lambda(\epsilonNu,\bU)$ is the neutrino absorption mean free path.
They have the following relation:
\begin{equation}
\dfrac{1}{\lambda(\epsilonNu,\bU)} = e^{(\epsilonNu-\mu_{\nu})/k_{\mbox{\tiny B}}T} j(\epsilonNu,\bU) .
\end{equation}
Therefore,
\begin{equation}
\dfrac{1}{\lambda} = e^{(\epsilonNu-\mu_{\nu})/k_{\mbox{\tiny B}}T} (j_{nucleon} + j_{nuclear} ) = (\dfrac{1}{\lambda})_{nucleon} + (\dfrac{1}{\lambda})_{nuclear}.
\end{equation}
The two terms of electron-neutrino absorption on nucleons are
 \begin{align}
    (\dfrac{1}{\lambda})_{nucleon}(\epsilonNu,\bU) & = \dfrac{G^2}{\pi} \eta_{np}(g_V^2+3g_A^2)[1-F_e(\varepsilon+Q)](\varepsilon+Q)^2[1-\dfrac{M^2_e}{(\varepsilon+Q)^2}]^{1/2},\\
    j_{nucleon}(\epsilonNu,\bU) &= \dfrac{G^2}{\pi}\eta_{pn}(g_V^2+3g_A^2)F_e(\varepsilon+Q)(\varepsilon+Q)^2[1-\dfrac{M^2_e}{(\varepsilon+Q)^2}]^{1/2}.
\end{align}
And the two terms of electron-neutrino absorption on nuclear are
\begin{align}
    (\dfrac{1}{\lambda})_{nuclear}(\epsilonNu,\bU) & = \dfrac{G^2}{\pi} n_A e^{\beta (\mu_n -\mu_p -Q')} g^2_A \dfrac{2}{7} N_p(Z) N_n(N)[1-F_e(\varepsilon+Q')](\varepsilon+Q')^2[1-\dfrac{M_e^2}{(\varepsilon+Q')^2}]^{1/2} ,\\
    j_{nuclear}(\epsilonNu,\bU) &=\dfrac{G^2}{\pi} n_A g^2_A \dfrac{2}{7} N_p(Z) N_n(N)F_e(\varepsilon+Q')(\varepsilon+Q')^2[1-\dfrac{M_e^2}{(\varepsilon+Q')^2}]^{1/2} .
\end{align}

The total opacity $\kappa(\epsilonNu,\bU)=\chi(\epsilonNu,\bU)+\sigma(\epsilonNu,\bU)$, and $\sigma(\epsilonNu,\bU)$ is the scattering opacities.
